Cartograms with Dynamic Features

### 2022-06-04 paper/section/main.tex
drat: update flowchart

 {
  \begin{figure*}[tb!]
      \centering
      \includegraphics[width=\textwidth,height=0.95\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm.See \figref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \algoref{alg:UpdateLayout} for more detail.}
      \label{fig:flowchart}
  \end{figure*}

>>>>

 {
  \begin{figure*}[tb!]
      \centering
      \includegraphics[width=\textwidth,height=0.95\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm. See \figref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \algoref{alg:UpdateLayout} for more detail. For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
      \label{fig:flowchart}
  \end{figure*}
